---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# easylift

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/nahid18/easylift)](https://github.com/nahid18/easylift/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/nahid18/easylift)](https://github.com/nahid18/easylift/pulls)
<!-- badges: end -->

The goal of `easylift` is to perform genomic liftover given `GRanges` and `chain` file.

## Installation

<!-- Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install `easylift` from [Bioconductor](http://bioconductor.org/) using the following code: -->

<!-- ```{r 'install', eval = FALSE} -->
<!-- if (!requireNamespace("BiocManager", quietly = TRUE)) { -->
<!--     install.packages("BiocManager") -->
<!-- } -->

<!-- BiocManager::install("easylift") -->
<!-- ``` -->

Get the latest development version from [GitHub](https://github.com/nahid18/easylift) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("nahid18/easylift")
```
## Usage

First, import the libraries
```{r library, eval = requireNamespace('easylift', 'GenomicRanges')}
library("easylift")
library("GenomicRanges")
```

Then, execute the code below. 
This assumes you already downloaded the required chain file.

```{r example, eval = FALSE}
gr <- GRanges(seqname = Rle(paste("chr", 1, sep = "")),
              ranges = IRanges(start = 1, end = 200000))
genome(gr) <- "hg19"
to <- "hg38"
chain <- "hg19ToHg38.over.chain.gz"
lifted <- easylift(gr, to, chain)
```

## Citation

To cite package ‘easylift’ in publications use:

  Al Nahid A, Love M (2023). _easylift: An R package to perform
  genomic liftOver_. R package version 0.0.1,
  <https://github.com/nahid18/easylift>.


A BibTeX entry for LaTeX users is

```
  @Manual{,
    title = {easylift: An R package to perform genomic liftOver},
    author = {Abdullah {Al Nahid} and Michael Love},
    year = {2023},
    note = {R package version 0.0.1},
    url = {https://github.com/nahid18/easylift},
  }
```

Please note that the `easylift` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `easylift` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.



