---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# easylift

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/nahid18/easylift)](https://github.com/nahid18/easylift/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/nahid18/easylift)](https://github.com/nahid18/easylift/pulls)
<!-- badges: end -->

The goal of `easylift` is to perform genomic liftover given `GRanges` and `chain` file.

## Installation

Get the latest development version from [GitHub](https://github.com/nahid18/easylift) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("easylift")
```
## Usage

Import the libraries
```{r library, eval = FALSE}
library("easylift")
```

Call `easylift` with `GRanges` object, target genome and chain file.

```{r example, eval = FALSE}
gr <- GRanges(
  seqname = Rle(
    c("chr1", "chr2"), 
    c(100000, 100000)
  ),
  ranges = IRanges(
    start = 1, 
    end = 200000
  )
)
genome(gr) <- "hg19"
to <- "hg38"
chain <- "hg19ToHg38.over.chain.gz"

easylift(gr, to, chain)
```

To use `BiocFileCache` for the chain file, you can add it to the cache as follows:

```{r example2, eval = FALSE}
chain_file <- "/path/to/your/hg19ToHg38.over.chain.gz"
bfc <- BiocFileCache()
bfcadd(bfc, chain_file)
```
Then, you can use it in `easylift` like this:
```{r example3, eval = FALSE}
easylift(gr, "hg38")
```

## Citation

To cite package `easylift` in publications use:

  Al Nahid A, Love M (2023). _easylift: An R package to perform
  genomic liftover_. R package version 0.99.6,
  <https://github.com/nahid18/easylift>.


A BibTeX entry for LaTeX users is

```
  @Manual{,
    title = {easylift: An R package to perform genomic liftover},
    author = {Abdullah Al Nahid and Michael Love},
    year = {2023},
    note = {R package version 0.99.6},
    url = {https://github.com/nahid18/easylift},
  }
```

Please note that the `easylift` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `easylift` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.



