---
title: "Introduction to easylift package"
abstract: >
  An R package to perform genomic liftover between different genome assemblies with `GRanges` and `chain` file. Source Code: https://github.com/nahid18/easylift
author:
- name: Abdullah Al Nahid
  affiliation: 
  - Department of Biochemistry and Molecular Biology, Shahjalal University of Science and Technology, Sylhet-3114, Bangladesh
- name: Michael I. Love
  affiliation: 
  - Biostatistics Department, University of North Carolina-Chapel Hill, Chapel Hill, NC, USA
  - Genetics Department, University of North Carolina-Chapel Hill, Chapel Hill, NC, USA
  email: michaelisaiahlove@gmail.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
vignette: >
  %\VignetteIndexEntry{easylift}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
  BiocStyle::markdown()
```
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Getting Started

## Installation

```{r install, eval=FALSE}
BiocManager::install("nahid18/easylift")
```

## Import

```{r setup}
library("easylift")
library("GenomicRanges")
```

## Arguments

Create a `GRanges` object, assign a genome to it, and specify chain file

```{r example}
gr <- GRanges(seqname = Rle(paste("chr", 1, sep = "")),
              ranges = IRanges(start = 1, end = 200000))
genome(gr) <- "hg19"
to <- "hg38"

# you should next just point directly to a file on your machine.
# here, we use the `system.file()` function because this is a vignette
chain <- system.file("extdata/hg19ToHg38.over.chain.gz", package="easylift")

gr
```

## Run

```{r run}
easylift(gr, to, chain)
```

## Cache (optional)

If you have the chain file in cache with `BiocFileCache` package, you don't have to specify `chain` argument

```{r bioCache, eval=FALSE}
gr |> easylift("hg38")
```

# Citation

To cite package ‘easylift’ in publications use:

  Al Nahid A, Love M (2023). _easylift: An R package to perform
  genomic liftOver_. R package version 0.0.3,
  https://github.com/nahid18/easylift.

A BibTeX entry for LaTeX users is

```
  @Manual{,
    title = {easylift: An R package to perform genomic liftOver},
    author = {Abdullah Al Nahid and Michael Love},
    year = {2023},
    note = {R package version 0.0.3},
    url = {https://github.com/nahid18/easylift},
  }
```

Please note that the `easylift` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

# Code of Conduct

Please note that the `easylift` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

# Session information

```{r}
sessionInfo()
```
